Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Turn section on fundamentalism into a quote (for now)
Add new subsections to "Solution"
Extend "Problem"

@@

\begin{quote}
    TBD:
\begin{itemize}
    \item Motivate \verb|test-shouldbe|
    \item Motivate \verb|shouldThrow|
    \item \emph{optional:} Motivate why it's important to integrate \doctest{} with
        Cabal.
    \item \emph{optional:} Motivate \verb|hspec-discover|
\end{itemize}
\end{quote}

@@

@@

Note that the authors are not fundamentalist.
If functions to be defined are simple enough,
we might implement them first withtout signatures.
And their signatures can be automatically
inserted by IDE (such as Emacs/vim with {\tt ghc-mod}) later
if Haskell compilers can infer correctly.
Also, we can copy-and-paste examples and their results
from Haskell interpreters to their Haddock markup.

>>>>

\item[spec]
    TBD: BDD terminology for test suite.

@@

\begin{quote}
    TBD:
\begin{itemize}
    \item Motivate \verb|test-shouldbe|
    \item Motivate \verb|shouldThrow|
    \item \emph{optional:} Motivate why it's important to integrate \doctest{} with
        Cabal.
    \item \emph{optional:} Motivate \verb|hspec-discover|
        It is common to have several files that contain \emph{specs}.
        And we want to be able to run them all together.  Hspec allows
        us combine specs together.  But this has to be done manually.
        Hspec does not provide a way to automatically discover and run
        all specs of a project.
\end{itemize}
\end{quote}

@@

\subsection{Combinators for expectations}
TBD
\subsection{Automatic discovery of specs}
TBD

@@

\begin{quote}
    TBD: @kazu: Do we need this to make our case?  I'm asking, because
    it will require some work to get the language right.

    Note that the authors are not fundamentalist.  If functions to be
    defined are simple enough, we might implement them first withtout
    signatures.  And their signatures can be automatically inserted by
    IDE (such as Emacs/vim with {\tt ghc-mod}) later if Haskell
    compilers can infer correctly.  Also, we can copy-and-paste
    examples and their results from Haskell interpreters to their
    Haddock markup.
\end{quote}
